### 2013-04-01 exam6/2.tex
BST problem.

 Binary tree problem

\textbf{Extra Credit}

>>>>

A \emph{binary search tree} is a lot like a binary tree in that a BST
is either a node, which contains an element and a left and right
subtree, or a leaf, which doesn't contain an element or subtrees.  The
difference between a binary tree and a binary \emph{search} tree is
that every leaf and node of a BST also contains a \texttt{Comparator},
and nodes have the following invariant: every element in the left
subtree is smaller (according to the comparator) than the element in
the node, which in turn is smaller than or equal (according to the
comparator) to every element in the right subtree.  (You can assume
the comparator in every leaf and node is the same for any given BST.)

\begin{enumerate}
\item Design class and interface definitions for binary search trees
  \texttt{BST<X>}.  Design the following method for binary search
  trees:
  \begin{verbatim}
  // Insert x into this BST, preserving the BST invariant
  BST<X> insert(X x);
\end{verbatim}

\ifrubric\else
\newpage
[Here is some more space for the previous problem.]
\fi

\newpage
\item Here's an idea for sorting a series of elements: take all of the
 elements and insert them into (an initially empty) binary search
 tree.  Now, assuming \texttt{BST<X>} implemented the
 \texttt{Iterable<X>} such that the iterator produced by
 \texttt{iterator()} visited the elements of the BST in increasing
 order (according to the comparator), then the elements could be retrieved
in sorted order.

Use this idea to implement a sorting method with the signature given
 below.  It should sort a given iterable object in ascending order
 according to a given comparator, producing the sorted list as an
 array list of elements.

You may assume \texttt{BST<X>} implements \texttt{Iterable<X>} correctly
and do not need to define this yourself (see the extra credit).

{\small
\begin{verbatim}
// Class of sorting methods
class Sort {
  // Produce an array list of elems sorted in ascending order by c
  <X> ArrayList<X> treeSort(Comparator<X> c, Iterable<X> elems) { 
    ... 
  }
}
\end{verbatim}}
\end{enumerate}

\ifrubric
\else
\newpage
[Here is some more space for the previous problem.]
\fi
\newpage
\newpage
\end{problem}
